Using traffic analysis to identify The Second Generation Onion Router

### 2010-12-29 thesis/experiment.tex
Started putting in summaries of software, with quotes

>>>>

\chapter{Materials and Methods}

\section{Instruments and Apparatus}

The experiment described requires a number of computer systems and associated hardware to run the simulation and capture appropriate data. This equipment is described in the following chapter.

\section{Personal Computer}

\section{Hub/Unmanaged Router}
\section{Tor Software}
\section{'tcpdump' Software}
\section{Weka Software}
\section{VirtualBox Software}
\section{Ruby Software}

\section{Ubuntu Linux Software}

The Ubuntu Linux operating system is freely available Linux operating system
available for desktop personal computers.

\section{Selenium Software}

Selenium is a web testing framework with a number of components that allow
developers to write automated tests of web applications using most modern web
browsers \parencite{:2010ys}. Using the Selenium framework one can mimic the
actions of an actual user interacting with a web site.

\section{Firefox Software}

Firefox is a web browser developed by the Mozilla organization and freely
available for most desktop personal computers \parencite{mozilla}. It's strong
standards compliance \parencite{Hammond:2010fk} and popularity
\parencite{:2010kx,:2010vn} on the simulation platform make it an ideal candidate for
this experiment .

\section{OpenSSH Software}

\cite{Tucker:2010ly}
\cite{:2010zr}
\cite{:ve}

\section{Apache Software}

\cite{:qf}

\section{Sinatra Software}
